Progress Report on One Simulated Dataset

### 2023-10-12 Docs/ProgressReportSim.Rmd
update report

- Use fastGFPCA::reeval_efunctions. Cannot install the package so used the source code directly
- I would like to adjust use time points on the [0, 1] scale as evaluation points
- Also, take number of knots and order from the FPCA model in step 3 (knots = 35, p = 3)
- Do the same kind of projection to mean functions as well

@@

### Compared to biased eigenvalues

@@

### Scaled eigenfunctions and eigenvalues

- No need to scale mean functions

@@

- Time spent on one iteration: `r round(t_1sim, 2)` seconds
- Did debiased eigenvalues improve performance? The lines above look like so. I also wanna see the squared errors and AUC.
- Scaling eigenfunctions and values will change a prediction a little bit

@@

@@

- Looks like the debiased eigenvalues helped.
- Scaling, on the other hand, does seem to help in general. 
- But shouldn't scaling improve performance? 
- Also, it seems like the longer the observed track, the closer the three cases are.

>>>>

- Use fastGFPCA::reeval_efunctions. Cannot install the package so used the source code directly.
- I would like to use time points on the [0, 1] scale as evaluation points when creating basis functions.
- Also, take number of knots and order from the FPCA model in step 3 (knots = 35, cubic spline basis). 
- Do the same kind of projection to mean functions as well

@@

<!-- ### Compared to biased eigenvalues -->

@@

<!-- ### Scaled eigenfunctions and eigenvalues -->

@@

I would like to see if the following operations can improve predictive performance:

1. Debiasing eigenvalues from FPCA
2. Scale the eigenfunctions and debiased eigenvalues (from mgcv::bam) so that they are close to the true values for data generation

@@

- Time spent on one iteration: `r round(t_1sim, 2)` seconds
- Debiasing eigenvalues helped with prediction. Scaling eigenfunctiosn and eigenvalues, on the other hand, ended up being more complicated.

@@

- Looks like the debiased eigenvalues helped.
- Scaling, on the other hand, doesn't seem to help in general. But shouldn't scaling improve performance? 
- Also, it seems like the longer the observed track, the less different the performance is.
